{\fontfamily{ptm}\selectfont A Parameter Free Accelerated Proximal Gradient Method Without Restarting }

### 2024-12-12 Notebook LaTEX/Momentum Accelerations/paper3.tex
>w<, changes

\noindent{\bfseries 2010 Mathematics Subject Classification:}
Primary 65K10, 90c25, 90C30; Secondary 65Y20. 
\noindent{\bfseries Keywords: } Nesterov acceleration, Proximal point method.

@@

\section{Formulation of R-WAPG and its convergence rates}

@@

\section{R-WAPG covers variants of APG in the literatures}
    Many variants of the accelerated proximal gradient algorithm fits into the following form which we called ``abstract similar triangle". 
    \begin{proposition}[Abstract similar triangle form]\label{prop:abs-st-form}\;\\
        For all $k\ge 0$, iterates $(w_t, y_t, x_{t + 1}, z_{t + 1})$ satisfies recursively that: 
        \begin{align*}
            y_k &= (1 + \tau_k)^{-1}(v_k + \tau_k x_k),
            \\
            v_{k + 1} &= (1 + \xi_k)^{-1}(v_k + \xi_k y_k) - (1 + \xi_k)^{-1}\delta_k g_k,
            \\
            x_{k + 1} &= y_k - L^{-1} g_k. 
        \end{align*}
        If $1 + \xi_t + \tau_t = L\delta_t$. Then 
        $$
            v_{k + 1} - x_{k + 1} = (1 + \xi_t)^{-1}\tau_t(x_{k + 1} - x_k). 
        $$
        Which makes the algorithm a similar triangle form. 
    \end{proposition}
    \begin{proof}
        We are interested in identifying the conditions required for the sequence of $\xi_t, \tau_t, \delta_t$ such that there exists $\theta_t$ satisfying: 
        \begin{align*}
            x_{t + 1} - z_{t + 1} 
            &= \theta_t(z_{t + 1} - z_t)
        \end{align*}
        To verify, do 
        \begin{align*}
            x_{t + 1} &= 
            (1 + \xi_t)^{-1}(x_t + \xi_t y_t - \delta_t \mathcal G_L(y_t))
            \\
            & \textcolor{gray}{
                x_t = (1 + \tau_t)y_t - \tau_t z_t
            }
            \\
            &= 
            (1 + \xi_t)^{-1}((1 + \tau_t)y_t - \tau_t z_t + \xi_t y_t - \delta_t \mathcal G_L(y_t))
            \\
            &= 
            (1 + \xi_t)^{-1}((1 + \tau_t + \xi_t)y_t - \tau_t z_t - \delta_t \mathcal G_L(y_t))
            \\
            x_{t + 1} - z_{t + 1}
            &= 
            (1 + \xi_t)^{-1}((1 + \tau_t + \xi_t)y_t - \tau_t z_t - \delta_t \mathcal G_L(y_t))
            - (y_t - L^{-1}\mathcal G_Ly_t)
            \\
            &= 
            (1 + \xi_t)^{-1}(\tau_ty_t - \tau_t z_t - \delta_t \mathcal G_L(y_t))
            + L^{-1}\mathcal G_Ly_t
            \\
            &= 
            (1 + \xi_t)^{-1}
            \left(
                \tau_ty_t - \tau_t z_t + (L^{-1}(1 + \xi_t) - \delta_t) \mathcal G_L(y_t)
            \right)
            \\
            &= 
            (1 + \xi_t)^{-1}\tau_t
            \left(
                y_t - z_t + 
                \tau_t^{-1}(L^{-1}(1 + \xi_t) - \delta_t) \mathcal G_L(y_t)
            \right)
        \end{align*}
        The RHS is can be verified through 
        \begin{align*}
            z_{t + 1} - z_t &= 
            y_t - L^{-1}\mathcal G_L(y_t) - z_t
            \\
            &= (y_t - z_t) - L^{-1}\mathcal G_L(y_t). 
        \end{align*}
        It necessitates the condition: 
        \begin{align*}
            \tau_t^{-1}(L^{-1}(1 + \xi_t) - \delta_t) 
            &= - L^{-1}
            \\
            (1 + \xi_t) - L\delta_t
            &= 
            - \tau_t
            \\
            1 + \xi_t + \tau_t
            &=
            L\delta_t. 
        \end{align*}
        Which allows for: 
        \begin{align*}
            x_{t + 1} - z_{t + 1} &= 
            (1 + \xi_t)^{-1}\tau_t
            \left(y_t - z_t - L^{-1}\mathcal G_L(y_t)\right) 
            = 
            (1 + \xi_t)^{-1}\tau_t(z_{t + 1} - z_t). 
        \end{align*}
    \end{proof}

@@

            Choose any $\gamma_0 \in (0, 1)$ as the initial condition for R-WAPG to produce vectors sequence $(y_i)_{i \in \N}, (x_i)_{i \in \N}, (v_i)_{i \in \N}$ and $(\rho_k)_{i \in \N}, (\alpha_k)_{i \in \N}$. 

@@

                \right) - \frac{1}{L\alpha_{k}}\mathcal G_L y_k, 
                L &\alpha_k^2 = (1 - \alpha_k)L \rho_{k - 1}\alpha_{k - 1}^2 + \mu \alpha_k. 

@@

            Observe that this is fits the abstract similar triangle form described in Proposition \ref{prop:abs-st-form} perfectly by exchanging $x_k$ with $z_k$, $v_k$ with $x_k$. 
        \begin{definition}[R-WAPG intermediate representation]\label{def:r-wapg-intermediate}\;\\

@@

            Assume that the auxiliary sequence $\rho_k$ has $\rho_k \alpha_k^2 < 1$ for all $k \ge 0$. 
            The algorithm generate sequence of vector iterates $(x_k, v_k, y_k)_{k \ge0}$ by 

@@

                \right) - \frac{1}{L\alpha_{k}}\mathcal G_L y_k, 

@@

            Given any sequence $(\alpha_i)_{i \ge k}$ such that $\alpha_i \in (0, 1)$, $\rho_k \ge 0$ for all $0 \le i \le k$ and $0 < L\alpha_k^2 = (1 - \alpha_k)L\rho_{k - 1}\alpha_{k - 1}^2 + \alpha_k \mu$.  
            Let $(x_k, y_k, v_k)$ to be generated as specified by Algorithm 2.2 by such $(\alpha_k)_{k \ge0}$. Then iterate $(v_k)$ can be expressed without $y_k, v_k$ by: 

@@

    \begin{proposition}[R-WAPG fits into Momentum Form]\label{prop:wapg-momentum-form}
        \;\\
        Suppose any sequence $(\alpha_k)_{k \ge 0}, (\rho_k)_{k \ge0}$ satisfies recursively the conditions
        $L\alpha_k^2 = (1 - \alpha_k)L\rho_{k - 1}\alpha_{k - 1}^2 + \alpha_k \mu$ where $\rho_{k} \ge 0\; \forall k \ge0$. 
        Assume that $0 \le \mu < L$. 
        If $\alpha_k$ is used in the similar triangle form to generate the iterates $(x_k, y_k, v_k)$. 
        Then the iterates are algebraically equivalent to: 
        \begin{align*}
            x_{k + 1} &= y_k - L^{-1}\mathcal G_Ly_k, 
            \\
            y_{k + 1} &= 
            x_{k + 1} + 
            \frac{\rho_k\alpha_k(1 - \alpha_k)}{\rho_k\alpha_k^2 + \alpha_{k + 1}}(x_{k + 1} - x_k). 
        \end{align*}
        In the special case when $\mu = 0$, the momentum term admits simpler representation 
        \begin{align*}
        \frac{\rho_k\alpha_k(1 - \alpha_k)}{\rho_k\alpha_k^2 + \alpha_{k + 1}}
        & = \alpha_{k + 1}(\alpha_k^{-1} - 1). 
        \end{align*}
    \end{proposition}
    \begin{proof}

        Start by considering the update rule for $v_k$ from the similar triangle form of WAPG which is: 
            x_{k + 1} + (\alpha_k^{-1} - 1)(x_{k + 1} - x_k)
            (L \alpha_{k + 1} - \mu)v_{k + 1} 
            (L \alpha_{k + 1} - \mu)x_{k + 1} + (L\alpha_{k + 1} - \mu)(\alpha_k^{-1} - 1)(x_{k + 1} - x_k). 
        Next, we simplify the update for the iterates $y_{k}$ by the similar triangle form of R-WAPG. 

@@

            \frac{L - \mu}{L\alpha_k - \mu} 
            \frac{L\alpha_k - \mu}{L - \mu} v_k
            \frac{L - L \alpha_k}{L - \mu} x_k
            &= (L - \mu)^{-1}((L \alpha_k - \mu)v_k + (L - L \alpha_k)x_k). 
        Now considering substituting $v_{k + 1}$ into $y_{k + 1}$ so it has: 
            y_{k + 1} &= 
            (L - \mu)^{-1}((L\alpha_{k + 1} - \mu)v_{k + 1} + (L - L \alpha_{k + 1})x_{k + 1})
            &= (L - \mu)^{-1}
                (L\alpha_{k + 1} - \mu)x_{k + 1} + 
                (L\alpha_{k + 1} - \mu)(\alpha_k^{-1} - 1)(x_{k + 1} - x_k)
                + (L - L \alpha_{k + 1})x_{k + 1}
            (L - \mu)^{-1}
                (L - \mu)x_{k + 1} + (L\alpha_{k + 1} - \mu)(\alpha_k^{-1} - 1)(x_{k + 1} - x_k)
            &= x_{k + 1} + \frac{(L\alpha_{k + 1} - \mu)(\alpha_k^{-1} - 1)}{L - \mu}(x_{k + 1} - x_k). 
        The coefficient for $(x_{k + 1} - x_k)$ needs some works to formulate it without the parameter $\mu, L$. 
        To do that we have: 
            \frac{(L\alpha_{k + 1} - \mu)(\alpha_k^{-1} - 1)}{L - \mu}
            &= \frac{(L\alpha_{k + 1} - \mu)\alpha_k(1 - \alpha_k)}{\alpha_k^2(L - \mu)}
            \alpha_k(1 - \alpha_k)
                \frac{\alpha_k^2(L - \mu)}{L\alpha_{k + 1} - \mu}
            &= \alpha_k(1 - \alpha_k)
                \frac{L\alpha_k^2 - \mu\alpha_k^2}{L\alpha_{k + 1} - \mu}
            \alpha_k(1 - \alpha_k)
            \rho_k\left(
                \frac{L\rho_k\alpha_k^2 - \mu\rho_k\alpha_k^2}{L\alpha_{k + 1} - \mu}
            \rho_k\alpha_k(1 - \alpha_k)
                \frac{(L\alpha_{k + 1} - \mu)(\rho_k\alpha_k^2 + \alpha_{k + 1})}
                {L\alpha_{k + 1} - \mu}
            &= \frac{\rho_k\alpha_k(1 - \alpha_k)}{\rho_k\alpha_k^2 + \alpha_{k + 1}}.
        Going from the left to right on the fourth equality, we used $L\alpha_{k + 1}^2 = (1 - \alpha_{k + 1})\rho_kL\alpha_k^2 + \mu \alpha_{k + 1}$ with 
            L \rho_k \alpha_k^2 - \mu \rho_k \alpha_k^2 
            (1 - \alpha_{k + 1})L \rho_k \alpha_k^2 + \alpha_{k + 1} L \rho_k \alpha_k^2 - \mu \rho_k \alpha_k^2
            ((1 - \alpha_{k + 1})L \rho_k \alpha_k^2 + \mu \alpha_{k + 1}) - \mu\alpha_{k + 1} + \alpha_{k + 1} L \rho_k \alpha_k^2 - \mu \rho_k \alpha_k^2
            &= L \alpha_{k + 1}^2 - \mu\alpha_{k + 1} + \alpha_{k + 1}L\rho_k\alpha_k^2 - \mu \rho_k \alpha_k^2
            L\alpha_{k + 1}(\alpha_{k + 1} + \rho_k \alpha_k^2) - \alpha_{k + 1}\mu - \mu \rho_k \alpha_k^2
            &= (L \alpha_{k + 1} - \mu)(\alpha_{k + 1} + \rho_k \alpha_k^2). 
        When $\mu = 0$, things simplify. 
        Consider that $\alpha_{k +1}^2 = (1 - \alpha_{k + 1})\alpha_k^2$. 
            \frac{\rho_k\alpha_k(1 - \alpha_k)}{\rho_k\alpha_k^2 + \alpha_{k + 1}}
            \frac{\rho_k\alpha_{k + 1}\alpha_k(1 - \alpha_k)}
            {\rho_k\alpha_{k + 1}\alpha_k^2 + \alpha_{k + 1}^2}
            \frac{\rho_k\alpha_{k + 1}\alpha_k(1 - \alpha_k)}
            {\rho_k\alpha_{k + 1}\alpha_k^2 + \rho_k(1 - \alpha_{k + 1})\alpha_k^2}
            &= \frac{\rho_k\alpha_{k + 1}\alpha_k(1 - \alpha_k)}{\rho_k\alpha_k^2}
            &= \alpha_{k + 1}(\alpha_k^{-1} - 1). 
        There exists a choice of $\rho_k \in [0, 1), \mu = 0$ such that the above algorithm is equivalent to Chambolle Dossal 2015 \cite{chambolle_convergence_2015}. 
        When $\rho_k = 1$, this becomes just FISTA \cite{beck_fast_2009}. 
        When $L > \mu > 0$, then choosing $\rho_k = 1$ yields equation 
            L \alpha_{k + 1}^2 = (1- \alpha_{k + 1})L \alpha_k^2 + \alpha_{k + 1} \mu. 
        Here, if we assume sequence $\alpha_k$ is constant, then $\alpha_k = \sqrt{\mu/L}$ is a solution to the above iterative equation. 
        Substituting it back to the momentum form of R-WAPG, we recovers the V-FISTA algorithm, which appears as (10.7.7) in Beck's Book \cite{beck_first-order_2017}. 

>>>>

\noindent{\bfseries 2010 Mathematics Subject Classification:}
Primary 65K10, 90c25, 90C30; Secondary 65Y20. 
\noindent{\bfseries Keywords: } Nesterov acceleration, Proximal point method. 
\section{Introduction}
    \subsection{Literature reviews}
    \subsection{Contributions}
        Our contributions are two folds.

        We present a theoretical unification through the formulation of ``Relaxed weak accelerated proximal gradient algorithm (R-WAPG)'' which we invented. 
        It unifies convergence claim for accelerated method for the strongly convex objective and Lipschitz smooth but non-strongly convex case and it relaxes the conditions on the momentum sequence.

        We connect the theories and practice by pointing out one practical exploits inspired the convergence proof of the algorithm which we called ``Spectral Momentum''. 
        Numerical experiments are conducted to illustrate the theoretical convergence of R-WAPG and the performance of Spectral Momentum in with applications.

@@

\section{Formulation of R-WAPG and its convergence rates}
    Definition \ref{def:wapg} is an algorithm which generates iterates $(x_k, y_k, v_k)$ and admits potential convergence claim using Proposition \ref{prop:stepwise-lyapunov}. 
    It is the backbone of multiple accelerated first order method in the literatures which fits all variants under the same convergence claim.

@@

\section{Equivalent representations of R-WAPG}
    This section reduces Definition \ref{def:wapg} into simpler forms that are comparable to what commonly appears in the literatures. 
    Proposition \ref{prop:wapg-first-equivalent-repr} simplifies Definition \ref{def:wapg} for the specific initial conditions $\gamma_0 \in(0, 1)$ and finds a representation without auxiliary sequence $\gamma_k, \hat \gamma_k$. 
    Definition \ref{def:r-wapg-intermediate} states the first simplified form of the R-WAPG algorithm which we call: ``R-WAPG intermediate form''. 
    Following a similar pattern, Proposition \ref{prop:wagp-st-form}, \ref{prop:wagp-st-form} states two more equivalent representations under R-WAPG intermediate form which are formulated as Definition \ref{def:r-wapg-st-form}, \ref{def:r-wapg-momentum-form}.

    To start, the following proposition on ``abstract similar triangle form'' were made to simplify arguments and notations to make nicer proofs.

    \begin{proposition}[Abstract similar triangle form]\label{prop:abs-st-form}\;\\
        For all $k\ge 0$, iterates $(w_t, y_t, x_{t + 1}, z_{t + 1})$ satisfies recursively that: 
        \begin{align*}
            y_k &= (1 + \tau_k)^{-1}(v_k + \tau_k x_k),
            \\
            v_{k + 1} &= (1 + \xi_k)^{-1}(v_k + \xi_k y_k) - (1 + \xi_k)^{-1}\delta_k g_k,
            \\
            x_{k + 1} &= y_k - L^{-1} g_k. 
        \end{align*}
        If $1 + \xi_t + \tau_t = L\delta_t$. Then 
        $$
            v_{k + 1} - x_{k + 1} = (1 + \xi_t)^{-1}\tau_t(x_{k + 1} - x_k). 
        $$
        Which makes the algorithm a similar triangle form. 
    \end{proposition}
    \begin{proof}
        We are interested in identifying the conditions required for the sequence of $\xi_t, \tau_t, \delta_t$ such that there exists $\theta_t$ satisfying: 
        \begin{align*}
            x_{t + 1} - z_{t + 1} 
            &= \theta_t(z_{t + 1} - z_t)
        \end{align*}
        To verify, do 
        \begin{align*}
            x_{t + 1} &= 
            (1 + \xi_t)^{-1}(x_t + \xi_t y_t - \delta_t \mathcal G_L(y_t))
            \\
            & \textcolor{gray}{
                x_t = (1 + \tau_t)y_t - \tau_t z_t
            }
            \\
            &= 
            (1 + \xi_t)^{-1}((1 + \tau_t)y_t - \tau_t z_t + \xi_t y_t - \delta_t \mathcal G_L(y_t))
            \\
            &= 
            (1 + \xi_t)^{-1}((1 + \tau_t + \xi_t)y_t - \tau_t z_t - \delta_t \mathcal G_L(y_t))
            \\
            x_{t + 1} - z_{t + 1}
            &= 
            (1 + \xi_t)^{-1}((1 + \tau_t + \xi_t)y_t - \tau_t z_t - \delta_t \mathcal G_L(y_t))
            - (y_t - L^{-1}\mathcal G_Ly_t)
            \\
            &= 
            (1 + \xi_t)^{-1}(\tau_ty_t - \tau_t z_t - \delta_t \mathcal G_L(y_t))
            + L^{-1}\mathcal G_Ly_t
            \\
            &= 
            (1 + \xi_t)^{-1}
            \left(
                \tau_ty_t - \tau_t z_t + (L^{-1}(1 + \xi_t) - \delta_t) \mathcal G_L(y_t)
            \right)
            \\
            &= 
            (1 + \xi_t)^{-1}\tau_t
            \left(
                y_t - z_t + 
                \tau_t^{-1}(L^{-1}(1 + \xi_t) - \delta_t) \mathcal G_L(y_t)
            \right)
        \end{align*}
        The RHS is can be verified through 
        \begin{align*}
            z_{t + 1} - z_t &= 
            y_t - L^{-1}\mathcal G_L(y_t) - z_t
            \\
            &= (y_t - z_t) - L^{-1}\mathcal G_L(y_t). 
        \end{align*}
        It necessitates the condition: 
        \begin{align*}
            \tau_t^{-1}(L^{-1}(1 + \xi_t) - \delta_t) 
            &= - L^{-1}
            \\
            (1 + \xi_t) - L\delta_t
            &= 
            - \tau_t
            \\
            1 + \xi_t + \tau_t
            &=
            L\delta_t. 
        \end{align*}
        Which allows for: 
        \begin{align*}
            x_{t + 1} - z_{t + 1} &= 
            (1 + \xi_t)^{-1}\tau_t
            \left(y_t - z_t - L^{-1}\mathcal G_L(y_t)\right) 
            = 
            (1 + \xi_t)^{-1}\tau_t(z_{t + 1} - z_t). 
        \end{align*}
    \end{proof}

@@

            Choose any $\gamma_0 \in (0, 1)$ as the initial condition for R-WAPG (Definition \ref{def:wapg}) to produce vectors sequence $(y_i)_{i \in \N}, (x_i)_{i \in \N}, (v_i)_{i \in \N}$ and $(\rho_k)_{i \in \N}, (\alpha_k)_{i \in \N}$. 

@@

                \right) - \frac{1}{L\alpha_{k}}\mathcal G_L y_k. 

@@

        \begin{definition}[R-WAPG intermediate form]\label{def:r-wapg-intermediate}\;\\

@@

            The algorithm generate sequence of vector iterates $(x_k, v_k, y_k)_{k \ge0}$ by the procedures: 
                \text{find }& \rho_{k - 1}: 0 < \rho_{k - 1} < \alpha_{k - 1}^{-2},

@@

                \right) - \frac{1}{L\alpha_{k}}\mathcal G_L y_k. 

@@

            Let iterates $(x_k, v_k, y_k)_{k \ge 0}$ and sequence $(\alpha_k, \rho_k)_{k \ge0}$ be given by Definition \ref{def:r-wapg-intermediate}. 
            Then for all $k \ge0$, iterate $(v_k)_{k \ge 0}, (x_k)_{k \ge 0}, (y_k)_{k \ge0}$ are algebraically equivalent to: 

@@

    \begin{definition}[R-WAPG similar triangle form]\label{def:r-wapg-st-form}
        The algorithm generate sequence of vector iterates $(x_k, v_k, y_k)_{k \ge0}$ by the procedures: 
            \text{find }& \rho_{k - 1}: 0 < \rho_{k - 1} < \alpha_{k - 1}^{-2},

@@

            x_{k + 1} + (\alpha_k^{-1} -1)(x_{k + 1} - x_k). 

    \begin{proposition}[Third equivalent representation of R-WAPG]\label{prop:r-wapg-momentum-repr}
        \;\\
        Let sequence $(\alpha_k, \rho_k)_{k \ge0}$ and iterates $(x_k, v_k, y_k)_{k\ge 0}$ given by R-WAPG intermediate form (Definition \ref{def:r-wapg-st-form}). 
        Then the iterates are algebraically equivalent to: 
        \begin{align*}
            x_{k + 1} &= y_k - L^{-1}\mathcal G_Ly_k, 
            \\
            y_{k + 1} &= 
            x_{k + 1} + 
            \frac{\rho_k\alpha_k(1 - \alpha_k)}{\rho_k\alpha_k^2 + \alpha_{k + 1}}(x_{k + 1} - x_k). 
        \end{align*}
        In the special case when $\mu = 0$, the momentum term admits simpler representation 
        \begin{align*}
        \frac{\rho_k\alpha_k(1 - \alpha_k)}{\rho_k\alpha_k^2 + \alpha_{k + 1}}
        & = \alpha_{k + 1}(\alpha_k^{-1} - 1). 
        \end{align*}
    \end{proposition}

    \begin{proof}
        Start by considering the update rule for $v_k$ from the similar triangle form of WAPG which is: 
        \begin{align*}
            v_{k + 1} &= 
            x_{k + 1} + (\alpha_k^{-1} - 1)(x_{k + 1} - x_k)
            \\
            \iff 
            (L \alpha_{k + 1} - \mu)v_{k + 1} 
            &= 
            (L \alpha_{k + 1} - \mu)x_{k + 1} + (L\alpha_{k + 1} - \mu)(\alpha_k^{-1} - 1)(x_{k + 1} - x_k). 
        \end{align*}
        Next, we simplify the update for the iterates $y_{k}$ by the similar triangle form of R-WAPG. 
        \begin{align*}
            y_k &= 
            \left(
                1 + \frac{L - L\alpha_k}{L\alpha_k - \mu}
            \right)^{-1}
            \left(
                v_k + 
                \left(\frac{L - L\alpha_k}{L\alpha_k - \mu} \right) x_k
            \right)
            \\
            &= 
            \left(
            \frac{L - \mu}{L\alpha_k - \mu} 
            \right)^{-1}
            \left(
                v_k + 
                \left(\frac{L - L\alpha_k}{L\alpha_k - \mu} \right) x_k
            \right)
            \\
            &= 
            \frac{L\alpha_k - \mu}{L - \mu} v_k
            + 
            \frac{L - L \alpha_k}{L - \mu} x_k
            \\
            &= (L - \mu)^{-1}((L \alpha_k - \mu)v_k + (L - L \alpha_k)x_k). 
        \end{align*}
        Now considering substituting $v_{k + 1}$ into $y_{k + 1}$ so it has: 
        {\small
        \begin{align*}
            y_{k + 1} &= 
            (L - \mu)^{-1}((L\alpha_{k + 1} - \mu)v_{k + 1} + (L - L \alpha_{k + 1})x_{k + 1})
            \\
            &= (L - \mu)^{-1}
            \left(
                (L\alpha_{k + 1} - \mu)x_{k + 1} + 
                (L\alpha_{k + 1} - \mu)(\alpha_k^{-1} - 1)(x_{k + 1} - x_k)
                + (L - L \alpha_{k + 1})x_{k + 1}
            \right)
            \\
            &= 
            (L - \mu)^{-1}
            \left(
                (L - \mu)x_{k + 1} + (L\alpha_{k + 1} - \mu)(\alpha_k^{-1} - 1)(x_{k + 1} - x_k)
            \right)
            \\
            &= x_{k + 1} + \frac{(L\alpha_{k + 1} - \mu)(\alpha_k^{-1} - 1)}{L - \mu}(x_{k + 1} - x_k). 
        \end{align*}
        }

        The coefficient for $(x_{k + 1} - x_k)$ needs some works to formulate it without the parameter $\mu, L$. 
        To do that we have: 
        \begin{align*}
            \frac{(L\alpha_{k + 1} - \mu)(\alpha_k^{-1} - 1)}{L - \mu}
            &= \frac{(L\alpha_{k + 1} - \mu)\alpha_k(1 - \alpha_k)}{\alpha_k^2(L - \mu)}
            \\
            &= 
            \alpha_k(1 - \alpha_k)
            \left(
                \frac{\alpha_k^2(L - \mu)}{L\alpha_{k + 1} - \mu}
            \right)^{-1}
            \\
            &= \alpha_k(1 - \alpha_k)
            \left(
                \frac{L\alpha_k^2 - \mu\alpha_k^2}{L\alpha_{k + 1} - \mu}
            \right)^{-1}
            \\
            &= 
            \alpha_k(1 - \alpha_k)
            \rho_k\left(
                \frac{L\rho_k\alpha_k^2 - \mu\rho_k\alpha_k^2}{L\alpha_{k + 1} - \mu}
            \right)^{-1}
            \\
            &= 
            \rho_k\alpha_k(1 - \alpha_k)
            \left(
                \frac{(L\alpha_{k + 1} - \mu)(\rho_k\alpha_k^2 + \alpha_{k + 1})}
                {L\alpha_{k + 1} - \mu}
            \right)^{-1}
            \\
            &= \frac{\rho_k\alpha_k(1 - \alpha_k)}{\rho_k\alpha_k^2 + \alpha_{k + 1}}.
        \end{align*}
        Going from the left to right on the fourth equality, we used $L\alpha_{k + 1}^2 = (1 - \alpha_{k + 1})\rho_kL\alpha_k^2 + \mu \alpha_{k + 1}$ with 
        \begin{align*}
            L \rho_k \alpha_k^2 - \mu \rho_k \alpha_k^2 
            &= 
            (1 - \alpha_{k + 1})L \rho_k \alpha_k^2 + \alpha_{k + 1} L \rho_k \alpha_k^2 - \mu \rho_k \alpha_k^2
            \\
            &= 
            ((1 - \alpha_{k + 1})L \rho_k \alpha_k^2 + \mu \alpha_{k + 1}) - \mu\alpha_{k + 1} + \alpha_{k + 1} L \rho_k \alpha_k^2 - \mu \rho_k \alpha_k^2
            \\
            &= L \alpha_{k + 1}^2 - \mu\alpha_{k + 1} + \alpha_{k + 1}L\rho_k\alpha_k^2 - \mu \rho_k \alpha_k^2
            \\
            &= 
            L\alpha_{k + 1}(\alpha_{k + 1} + \rho_k \alpha_k^2) - \alpha_{k + 1}\mu - \mu \rho_k \alpha_k^2
            \\
            &= (L \alpha_{k + 1} - \mu)(\alpha_{k + 1} + \rho_k \alpha_k^2). 
        \end{align*}
        When $\mu = 0$, things simplify. 
        Consider that $\alpha_{k +1}^2 = (1 - \alpha_{k + 1})\alpha_k^2$. 
        \begin{align*}
            \frac{\rho_k\alpha_k(1 - \alpha_k)}{\rho_k\alpha_k^2 + \alpha_{k + 1}}
            &= 
            \frac{\rho_k\alpha_{k + 1}\alpha_k(1 - \alpha_k)}
            {\rho_k\alpha_{k + 1}\alpha_k^2 + \alpha_{k + 1}^2}
            \\
            &= 
            \frac{\rho_k\alpha_{k + 1}\alpha_k(1 - \alpha_k)}
            {\rho_k\alpha_{k + 1}\alpha_k^2 + \rho_k(1 - \alpha_{k + 1})\alpha_k^2}
            \\
            &= \frac{\rho_k\alpha_{k + 1}\alpha_k(1 - \alpha_k)}{\rho_k\alpha_k^2}
            \\
            &= \alpha_{k + 1}(\alpha_k^{-1} - 1). 
        \end{align*}
    \end{proof}

    \begin{definition}[R-WAPG momentum form]\label{def:r-wapg-momentum-form}
        Initialize any $\alpha_0 \in (0, 1)$. 
        The algorithm generates iterates $(v_k, x_k, y_k)$ and auxiliary sequence $(\rho_k)_{k \ge0}$ by the following procedures: 
        \begin{align*}
            \text{find }& \rho_{k - 1}: 0 < \rho_{k - 1} < \alpha_{k - 1}^{-2},
            \\
            \alpha_k &= 
            \frac{1}{2}\left(
            \frac{\mu}{L} - \rho_{k - 1}\alpha_{k - 1}^2 
            +
            \sqrt{(\rho_{k - 1}\alpha_{k - 1}^2 - \mu/L)^2 + 4\rho_{k - 1}\alpha_{k - 1}^2}
            \right), 
            \\
            x_{k + 1} &= y_k - L^{-1}\mathcal G_Ly_k, 
            \\
            y_{k + 1} &= 
            x_{k + 1} + 
            \frac{\rho_k\alpha_k(1 - \alpha_k)}{\rho_k\alpha_k^2 + \alpha_{k + 1}}(x_{k + 1} - x_k). 
        \end{align*}
        In the special case $\mu = 0$, the momentum term can be represented without relaxation parameter $\rho_k$: 
        $$
        \frac{\rho_k\alpha_k(1 - \alpha_k)}{\rho_k\alpha_k^2 + \alpha_{k + 1}} 
        = \alpha_{k + 1}(\alpha_k^{-1} - 1).  
        $$

    \end{definition}
    \begin{remark}
        \textcolor{red}
        {
        There exists a choice of $\rho_k \in [0, 1), \mu = 0$ such that the above algorithm is equivalent to Chambolle Dossal 2015 \cite{chambolle_convergence_2015}. 
        When $\rho_k = 1$, this becomes just FISTA \cite{beck_fast_2009}. 
        When $L > \mu > 0$, then choosing $\rho_k = 1$ yields equation 
        \begin{align*}
            L \alpha_{k + 1}^2 = (1- \alpha_{k + 1})L \alpha_k^2 + \alpha_{k + 1} \mu. 
        \end{align*}
        Here, if we assume sequence $\alpha_k$ is constant, then $\alpha_k = \sqrt{\mu/L}$ is a solution to the above iterative equation. 
        Substituting it back to the momentum form of R-WAPG, we recovers the V-FISTA algorithm, which appears as (10.7.7) in Beck's Book \cite{beck_first-order_2017}. 
        }
    \end{remark}

\subsection{Representing algorithms in the literatures via R-WAPG}
\subsection{The method of Spectral Momentum}
\subsection{Numerical experiments and applications}
